The Cluster Difference Imaging Photometric Survey (CDIPS). I. Method, Light Curves, and Planet Candidates from Sectors 6--8

### 2019-06-01 paper/ms.tex

\begin{figure*}[!ht]
  \gridline{\fig{astromresidual_hist.png}{0.5\textwidth}{}}
  \vspace{-0.8cm}
  \gridline{\fig{astromresidual_quiver.png}{0.5\textwidth}{}}
  \vspace{-0.8cm}
  \gridline{\fig{astromresidual_apertures.png}{0.5\textwidth}{}}
  \caption{
      {\it Top.} Histogram
      {\it Middle.} Vector
      {\it Bottom.} Apertures
  }
  \label{fig:xmatch_info}
\end{figure*}

@@

@@

107{,}647 of these stars, or about
10\% of the collection, have cluster memberships reported by
multiple authors.  The largest number of stars come from
\citealt{dias_proper_2014} (44.3\% of stars), \citealt{Kharchenko_et_al_2013}
(17.3\%), \citealt{cantat-gaudin_gaia_2018} (16.7\%), and \citealt{zari_3d_2018}
(11.1\%).
Stars reported in multiple catalogs have all available reference information
concatenated.  
The resulting CDIPS target star list is given in Table~N.

@@

@@

>>>>

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{star_catalog_mag_histogram_phot_rp_mean_mag.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    {\bf Cumulative counts of candidate cluster member stars a
    function of Gaia $Rp$-band magnitude.}
	\label{fig:cdips_targets}
	}
\end{figure}

@@

107{,}647 of these stars, or about
10\% of the collection, have cluster memberships reported by
multiple authors.  The largest number of stars come from
\citealt{dias_proper_2014} (44.3\% of stars), \citealt{Kharchenko_et_al_2013}
(17.3\%), \citealt{cantat-gaudin_gaia_2018} (16.7\%), and \citealt{zari_3d_2018}
(11.1\%).
Stars reported in multiple catalogs have all available reference information
concatenated.  
The resulting CDIPS target star list is given in Table~N.
The distribution of target star brightnesses is shown in
Figure~\ref{fig:cdips_targets}.

@@

\begin{figure*}[!ht]
	\gridline{\fig{astromresidual_hist.png}{0.5\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{astromresidual_quiver.png}{0.5\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{astromresidual_apertures.png}{0.5\textwidth}{}}
	\caption{
		{\it Top.} Histogram
		{\it Middle.} Vector
		{\it Bottom.} Apertures
	}
	\label{fig:astromresid}
\end{figure*}

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{cdf_T_mag.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Cumulative distribution of TESS-band magnitudes for CDIPS light curves.}
		\label{fig:cdf_T_mag}
	}
\end{figure}

\begin{figure}[!ht]
	\gridline{\fig{hrd_scat_all_CDIPS_LCs.png}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{hrd_scat_close_subset.png}{0.45\textwidth}{}}
	\caption{
		{\it Top.} Stellar properties of CDIPS stars with light curves in this data release.
		{\it Bottom.} Stellar properties of close CDIPS stars with light curves.
	}
	\label{fig:hrd}
\end{figure}
